\begin{enumerate}
		\item\textbf{Convenience}
		Preprocessing will be used on the client side to speed up system responsiveness and reduce work load on server nodes.
		
		\item\textbf{Privacy}
		It is crucial to our client that no one (not even administrators) should be able to see which user voted for which candidate. Encryption will be used to ensure privacy. By encrypting the from and to address of a vote, anonymity is ensured.
		
		\item\textbf{Availability}
		Fault detection, fault prevention and fault recovery will be used to ensure availability. Ping/echo commands will be used between nodes to detect possible node unavailability, active redundancy will be used for fault prevention and  for fault recovery a reset to a valid state will be used.
		
		\item\textbf{System Accountability}
		Exception classes will be used to ensure system accountability. As soon as a system error is encountered, an associated exception will be raised to determine the origin and cause of the error. This allows the system to transparently recover from expected and unexpected system errors.
		
		\item\textbf{Authentication and Control}
		Administrator and user authentication will be used to ensure the system isn't tampered with.
		
		\item\textbf{Eligibility}
		Administrators and users will go through an authorization process to ensure they can only do pre-determined alowed operations. For example a user aren't allowed to receive a vote, and a candidate is not allowed to send a vote.
		
		\item\textbf{Optimization}
		Database indexing will be used on the server's database when creating user and candidate accounts.
\end{enumerate}	