\begin{enumerate}
		\item \textbf{JHipster} is a Yeoman generator used to to create  Spring Boot and  AngularJS projects. This allows us to create a high performance and robust Java stack on the sever with Spring Boot and a modern, attractive front-end with AngularJS and Bootstrap.

		\item \textbf{Spring Boot} is one of the features of Spring Framework version 4.0 which gives us a way to proive Java applications quickly and simply through an embeded server – this means we can expose components such as REST services independently. This framework will prove usefull when deploying the Electronic Voting system. 
		
		\item \textbf{AngularJS} is a Javascript framework that be added to a HTML web page. AngularJS extends HTML attributes and binds data to HTML. It will be used to build highly interactive web pages for the Electronic Voting system. 
		
		\item \textbf{Bootsrap} is a HTML, CSS, and Javascript framework for developing responsive mobile-first web sites. We will use when writing the front-end of the web site and Android interface of the Electronic Voting system. 
		
		\item \textbf{Yeoman} allows us to kickstart a new project. It uses the “Yeoman workflow” which is a robust client-side stack comprising of tools and frameworks to help developers build web applications.
		
		The workflow comprises of 3 types of tools.  
		\begin{enumerate}
			\item \textbf{yo:} a scaffolding tool which helps generate and configure the outline of a new application. 
			\item \textbf{gulp:} a system build too used to preview and test a project. 
			\item \textbf{bower:} which is package management tool, also used for dependency management download and manage scripts.
		\end{enumerate} 
\end{enumerate} 